### 2017-06-12 PAPER/a_Thesis/Masterarbeit.tex

The time evolution of the density matrix is given by the von Neumann equation, which was coupled with a wave equation. $E_z(x,t)$ denotes the $z$-component of electric field (and also the assumed laser growth direction).  
\begin{subequations}
	\label{eq:dmequations}
 \begin{align}
	\frac{d\rho_{44}}{dt} &= J +i\frac{ez_{43}}{\hbar}E_z(\rho_{43}-\rho_{34}) + \sum_{j\neq 4} \frac{\rho_{jj}}{\tau_{j\rightarrow 4}}  - \frac{\rho_{44}}{\tau_{4}}, \\
	\frac{d\rho_{33}}{dt} &= -i\frac{ez_{43}}{\hbar}E_z(\rho_{43}-\rho_{34}) + \sum_{j\neq 3} \frac{\rho_{jj}}{\tau_{j\rightarrow 3}} - \frac{\rho_{33}}{\tau_{3}}, \\
	\frac{d\rho_{22}}{dt} &= \sum_{j\neq 2} \frac{\rho_{jj}}{\tau_{j\rightarrow 2}} - \frac{\rho_{22}}{\tau_{2}}, \\
	\frac{d\rho_{11}}{dt} &=  -J + \sum_{j\neq 1} \frac{\rho_{jj}}{\tau_{j\rightarrow 1}} - \frac{\rho_{11}}{\tau_{1}}, \\
	\frac{d\rho_{43}}{dt} &= - i\omega_{43}\rho_{43} + i\frac{ez_{43}}{\hbar}E_z(\rho_{44}-\rho_{33})-\Gamma_{\parallel 43}\rho_{43}.
 \end{align}
\end{subequations}
In Eqs. (\ref{eq:dmequations}) $\rho_{ij}$ denotes the $ij-$th density matrix element,  $z_{43}$ the optical transition's dipole moment, $e$ the elementary charge, $\hbar$ is the reduced Plank's constant. Also the parameter $1/\tau_{i\rightarrow j}$ is the net scattering rate from level $i$ to level $j$, calculated by our ensemble Monte Carlo code and incorporating, amongst others, longitudinal optical (LO) phonon, interface roughness and electron electron scattering mechanisms [cite]. Lastly $1/\tau_{i} = \sum_j 1/\tau_{i\rightarrow j}$ is the inverse lifetime of level $i$ and $\Gamma_{\parallel 43} = (\tau_4+\tau_3)/(2\tau_4\tau_3)+1/\tau^*$ is the dephasing rate of the optical transition, including lifetime broadening and a phenomenological pure dephasing $1/\tau^*$ rate due to intrasubband scattering processes [cite ANDO model]. The only scattering mechanism treated quantum mechanically is the optical transition between the upper and lower laser states. One can also fully coherently include resonant tunneling between the injector 1' and the upper laser state 4, which leads to a modified system of equations with larger number of independent variables and is thus more computationally demanding [cite]. Furthermore such an approach does not allow for the inclusion (without $k-$space discretization) of second order tunneling current into the simulations, which has been shown to be the origin of negative the differential conductivity and dispersive gain in quantum cascade lasers [].

In the tight-binding basis [cite], we can assume that the only electron transport channel across the QCL periods is via the resonant tunneling current between the injector and the upper laser state. When second order scattering effects are considered, under a few relaxing approximations, this tunneling current is given by [cite Terrazzi]
\begin{align}
\label{eq:current}
J &= en^s\frac{\Omega_{AC}^22\Gamma_{\parallel 1'4}}{\epsilon^2+4\Gamma_{\parallel 1'4}^2}\Big\{\Theta(\epsilon)(\rho_{11}-\rho_{44}e^{-|\hbar\epsilon|/k_BT}) \nonumber \\
&+\Theta(-\epsilon)(\rho_{11}e^{-|\hbar\epsilon|/k_BT}-\rho_{44})\Big\}.
\end{align}
In Eq. (\ref{eq:current}) $n^s$ denotes the sheet carrier density, $\Theta(\cdot)$ is the Heaviside function and the term $e^{-|\hbar\epsilon|/k_BT}$ denotes an effective "weight" factor modelling the assumption of thermalized $k$-space distribution of the injector and upper laser level electrons with the same thermal energy $k_BT$ in each subband.

@@

\subsection{Transmission line approach}
In this model, the vertical current component resulting from conductance of active region (n-doped semiconductor) under bias is calculated by current density J'(x,t) rather than by distributed conductance G'. Current density J(x,t) is nonuniform and bias dependent, it will be obtained by carrier transmission in optical part. Furthermore, although $v(x,t)$ and $i(x,t)$ in Eq. (\ref{eq:TLequation1}) and (\ref{eq:TLequation2}) are special for high frequency signal, they will be still valid if the transmission line was supplied additionally with a dc source. Therefore, the Telegrapher equations will be modified as following:

@@

In active mode-locking, QCL is supplied with source $ {V}_{S} $ which consists of a DC voltage source $ {V}_{DC} $ and an external RF source $ {V}_{RF} $. These two sources are combined through bias-T and the source voltaged can be expressed with $ {V}_{S}=V_{DC}+{V}_{RF} $. Due to existence of wire impedance there will be voltage drop on it, so the voltage at node 0 is not equal to source voltage $ {V}_{S} $.
% Boundary condition figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{images/pi_representation.pdf}
\caption{Schematic of cascade $\pi$ network representation and Thévenin equivalent circuit. }
\label{fig:BoundaryCondition}
\end{center}
\end{figure}

@@

\subsection{Distributed components}
The involvement of transmission line requires distributed component parameters. Except for distributed conductance G', which will be calculated in optical part, distributed resistance R', distributed inductance L' as well as distributed capacitance C' still need to be determined. They can be either calcuted as convertial passive components (plane resistor, parallel plane capacitor and inductor), or extracted from S-Parameter, which can be directly measured with network analyser. The former methode is simple and also don't require any extra tests, but could lead to large error due to neglection of fringe effect\cite{pillai1970fringing} as well as high frequency influence. The latter is based on experiments, so shows higher accuracy compared with former, but requires extra experiments as well as equipments, which is not always feasible for simulation research. In this work, these parameters of distributed components were eliminated by simple physical calculation assuming that device is with infinite length.

@@

Now that pure ac component cannot be simply obtained while resistance of transmission line at high frequency muss be taken into consideration, the problem was solved in another way by compromise. Instead of directly separating ac and dc component, temporal difference of ac component between adjacent time steps is considered to be feasible solution, which can be simply obtained by subtracting of Eqn. (\ref{eq:TLequation3}) at time ($n+\frac{1}{2}$) with that equation at previous time step ($n+\frac{1}{2}$), leading to:
\begin{equation}
\frac { { V }_{ j+1 }^{ n+\frac{3}{2} }-{ V }_{ j }^{ n+\frac{3}{2}}-({ V }_{ j+1 }^{ n+\frac{1}{2} }-{ V }_{ j }^{ n+\frac{1}{2} }) }{ \Delta x } \approx -L'\frac { { I }_{ j+\frac{1}{2} }^{ n+2 }-2{ I }_{ j+\frac{1}{2} }^{ n+1 }+{ I }_{ j+\frac{1}{2} }^{ n } }{ \Delta t } -R' (\widetilde{ i } _{ j+\frac{1}{2} }^{ n+\frac{3}{2} }-\widetilde{ i } _{ j+\frac{1}{2} }^{ n+\frac{1}{2} })\label{Eq:TL_substraction}
\end{equation}
The idea is, dc component as well as ac component with low frequency remains nearly unchanged after extremly short time step $\Delta t$ which is shorter than picosecond ($10^{-12}$ second) in this modeling. The variation of whole current at node $j+\frac{1}{2}$ is mainly resulting from variation of ac component of high frequency, which plays a key roll for increase of metal resistance. Hence, the variation of ac component can be approximately replaced with its corresponding variation of whole current. Besides, the current components have to be averaged in time with central difference method for sake of consistence, the same with $J_{j}^{n}$, leading to:
\begin{equation}
\tilde{ i }_{ j+\frac { 1 }{ 2 }  }^{ n+\frac{3}{2} }-\tilde{ i }_{ j+\frac { 1 }{ 2 }  }^{ n+\frac{1}{2} }\approx{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+\frac{3}{2} }-{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+\frac{1}{2} } \approx \frac{{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+2 }+{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+1 }-({ I }_{ j+\frac { 1 }{ 2 }  }^{ n+1 }+{ I }_{ j+\frac { 1 }{ 2 }  }^{ n })}{2}\label{Eq:ac_Current}
\end{equation}
Then substituting the approximate treatment above to Eqn. (\ref{Eq:TL_substraction}),  a equation with only voltage and whole current can be obtained:
\begin{equation}
\frac { { V }_{ j+1 }^{ n+\frac{3}{2} }-{ V }_{ j }^{ n+\frac{3}{2}}-({ V }_{ j+1 }^{ n+\frac{1}{2} }-{ V }_{ j }^{ n+\frac{1}{2} }) }{ \Delta x } \approx -L'\frac { { I }_{ j+\frac{1}{2} }^{ n+2 }-2{ I }_{ j+\frac{1}{2} }^{ n+1 }+{ I }_{ j+\frac{1}{2} }^{ n } }{ \Delta t } -R' \frac{{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+2 }-{ I }_{ j+\frac { 1 }{ 2 }  }^{ n }}{2}
\end{equation}

@@

\section{Results}
The amount of simulated iterations are 400 roundtrips, and during each simulation those important variables (e.g. optical field $E_{z}$, voltage, current, current density) at the middle point (x=L/2) of QCL were recorded after every time step.
\subsection{Characteristics of QCL}
Fig. \ref{fig:IVcurve} shows the voltage-current–luminance characteristics of the simulated QCL, which was obtained by supplying the QCL with a series of voltages ranging from 7.4 V to 10.8 V. The threshold voltage $V_{th}$ of the QCL is about 8.3 V, which means, under that there will be no lasing. Starting from $V_{th}$, the output emission will increase exponentially with higher voltage until tunneling phenomena occurs. At this area, QCL owns negative differential resistance (NDR) which is similar with tunneling diode. A large amount of injected electrons will directly pass active region through tunneling rather than transition from upper and lower laser levels accompanied with emission of phonons. Therefore, the increasing input voltage will not contribute to laser output power.

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{images/IVCURVE.pdf}
\caption{voltage-current–power characteristics of simulated QCL.}
\label{fig:IVcurve}
\end{center}
\end{figure}

Besides, the roundtrip frequency of this QCL was obtained by Fourier transformation of both its optical field and electrical voltage. As Fig. \ref{fig:beatnote_noRF} shows the beatnote of simulated QCL without RF source, its roundtrip frequency $f_{rt}$ is about 13.34 GHz.
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{images/beatnote_noRF.pdf}
\caption{Beatnote of the simulated QCL without RF source.}
\label{fig:beatnote_noRF}
\end{center}
\end{figure}

@@

Before simulation was carried out, firstly two parameters ($M_{A}$ and $f_{RF}$) have to be roughly defined. Although the function of RF source is known (Eq. (\ref{eq. V_RF})) and its power is proportional to square of its amplitude $M_{A}$, the injected power to QCL can still not be determined before simulation. Due to reflection as well as attenuation on wire between RF source and QCL, the injected power should be smaller than the power coming from RF source. But it is well known that theoretically optimal modulation frequency should exactly at roundtrip frequency. Therefore, simulations with different power and certain $f_{RF}$ were firstly carried out.
\subsubsection{Modulation with different power} 
Lack of sufficient modulation power, QCLs can still not be mode-locked even if modulation frequency is equal to $f_{rt}$. Therefore, modulations with different RF amplitude ($M_{A}$) was investigated, in which they all have the same modulation frequency and all the other parameters are the same as well. With increasing modulation power the side modes around main mode were strengthened (See Fig. \ref{fig:modA_Beatnote}) and will contribute to generate ultra short pulse. The bandwidth of frequency spectra was increasing consequently from 40 GHz to larger than 100 GHz. The optical field was mode-locked at modulation frequency $f_{RF}$, which is set at 13.9 GHz and a little higher than roundtrip frequency of this laser. 
%\begin{figure}[htbp]
%\begin{center}
%\includegraphics[scale=0.28]{images/modA_spectra.pdf}
%\caption{Normalized spectra in time as well as frequency domain with different modulation powers. modA denotes RF amplitude. $f_{RF}$ of RF source is at roundtrip frequency and QCL is bias by 8.6 kV/cm}
%\label{fig:modA_fspectra}
%\end{center}
%\end{figure}
\begin{figure*}[htbp]
  \centering
  \subfigure[]{\includegraphics[scale=0.9]{images/fa.pdf}}
  \subfigure[]{\includegraphics[scale=0.9]{images/Ba.pdf}}
\caption{(a)Frequency spectra of QCL emission with increasing modulation power from -8.5 dBm to -0.8 dBm. The simulated QCL has optical emission frequency of 3.8 THZ. (b) Beatnote of optical field $E_{z}$ (dashed blue line) and electrical voltage $V\_{TL}$ (red solid line).}
\label{fig:modA_Beatnote}
\end{figure*}

@@

Similar with in modulation with different powers, frequency spectra and beatnote were used to check the influence and whether mode-locking was achieved. If no RF source exists, QCL emits continuous light as expected and will show a clear single peak in frequency domain (See Fig. \ref{fig:modA_Beatnote}), which is at its emission frequency (in this case 3.8 THz). With increasing modulation frequency, the bandwidth of their frequency spectra were also increased and optical field was mode-locked at $f_{RF}$.
\begin{figure*}[htbp]
  \centering
  \subfigure[]{\includegraphics[scale=0.9]{images/f.pdf}}
  \subfigure[]{\includegraphics[scale=0.9]{images/B.pdf}}
\caption{(a)Frequency spectra of QCL emission with increasing modulation frequency from -8.5 dBm to -0.8 dBm. The simulated QCL has optical emission frequency of 3.8 THZ. (b) Beatnote of optical field $E_{z}$ (dashed blue line) and electrical voltage $V\_{TL}$ (red solid line).}
\label{fig:modA_Beatnote}
\end{figure*}

>>>>

The time evolution of the density matrix is given by the von Neumann equation, which was coupled with a wave equation. $E_z(x,t)$ denotes the $z$-component of electric field (and also the assumed laser growth direction).  
\begin{subequations}
	\label{eq:dmequations}
 \begin{align}
	\frac{d\rho_{44}}{dt} &= J +i\frac{ez_{43}}{\hbar}E_z(\rho_{43}-\rho_{34}) + \sum_{j\neq 4} \frac{\rho_{jj}}{\tau_{j\rightarrow 4}}  - \frac{\rho_{44}}{\tau_{4}}, \\
	\frac{d\rho_{33}}{dt} &= -i\frac{ez_{43}}{\hbar}E_z(\rho_{43}-\rho_{34}) + \sum_{j\neq 3} \frac{\rho_{jj}}{\tau_{j\rightarrow 3}} - \frac{\rho_{33}}{\tau_{3}}, \\
	\frac{d\rho_{22}}{dt} &= \sum_{j\neq 2} \frac{\rho_{jj}}{\tau_{j\rightarrow 2}} - \frac{\rho_{22}}{\tau_{2}}, \\
	\frac{d\rho_{11}}{dt} &=  -J + \sum_{j\neq 1} \frac{\rho_{jj}}{\tau_{j\rightarrow 1}} - \frac{\rho_{11}}{\tau_{1}}, \\
	\frac{d\rho_{43}}{dt} &= - i\omega_{43}\rho_{43} + i\frac{ez_{43}}{\hbar}E_z(\rho_{44}-\rho_{33})-\Gamma_{\parallel 43}\rho_{43}.
 \end{align}
\end{subequations}
In Eqn. (\ref{eq:dmequations}) $\rho_{ij}$ denotes the $ij-$th density matrix element,  $z_{43}$ the optical transition's dipole moment, $e$ the elementary charge, $\hbar$ is the reduced Plank's constant. Also the parameter $1/\tau_{i\rightarrow j}$ is the net scattering rate from level $i$ to level $j$, calculated by our ensemble Monte Carlo code and incorporating, amongst others, longitudinal optical (LO) phonon, interface roughness and electron electron scattering mechanisms [cite]. Lastly $1/\tau_{i} = \sum_j 1/\tau_{i\rightarrow j}$ is the inverse lifetime of level $i$ and $\Gamma_{\parallel 43} = (\tau_4+\tau_3)/(2\tau_4\tau_3)+1/\tau^*$ is the dephasing rate of the optical transition, including lifetime broadening and a phenomenological pure dephasing $1/\tau^*$ rate due to intrasubband scattering processes [cite ANDO model]. The only scattering mechanism treated quantum mechanically is the optical transition between the upper and lower laser states. One can also fully coherently include resonant tunneling between the injector 1' and the upper laser state 4, which leads to a modified system of equations with larger number of independent variables and is thus more computationally demanding [cite]. Furthermore such an approach does not allow for the inclusion (without $k-$space discretization) of second order tunneling current into the simulations, which has been shown to be the origin of negative the differential conductivity and dispersive gain in quantum cascade lasers [].

In the tight-binding basis [cite], we can assume that the only electron transport channel across the QCL periods is via the resonant tunneling current between the injector and the upper laser state. When second order scattering effects are considered, under a few relaxing approximations, this tunneling current is given by [cite Terrazzi]
\begin{align}
\label{eq:current}
J &= en^s\frac{\Omega_{AC}^22\Gamma_{\parallel 1'4}}{\epsilon^2+4\Gamma_{\parallel 1'4}^2}\Big\{\Theta(\epsilon)(\rho_{11}-\rho_{44}e^{-|\hbar\epsilon|/k_BT}) \nonumber \\
&+\Theta(-\epsilon)(\rho_{11}e^{-|\hbar\epsilon|/k_BT}-\rho_{44})\Big\}.
\end{align}
In Eqn. (\ref{eq:current}) $n^s$ denotes the sheet carrier density, $\Theta(\cdot)$ is the Heaviside function and the term $e^{-|\hbar\epsilon|/k_BT}$ denotes an effective "weight" factor modeling the assumption of thermalized $k$-space distribution of the injector and upper laser level electrons with the same thermal energy $k_BT$ in each subband.

@@

\subsection{Transmission line approach}
In this model, the vertical current component resulting from conductance of active region (n-doped semiconductor) under bias is calculated by current density J'(x,t) rather than by distributed conductance G'. Current density J(x,t) is nonuniform and bias dependent, it will be obtained by carrier transmission in optical part. Furthermore, although $v(x,t)$ and $i(x,t)$ in Eqn. (\ref{eq:TLequation1}) and (\ref{eq:TLequation2}) are special for high frequency signal, they will be still valid if the transmission line was supplied additionally with a dc source. Therefore, the Telegrapher equations will be modified as following:

@@

In active mode-locking, QCL is supplied with source $ {V}_{S} $ which consists of a DC voltage source $ {V}_{DC} $ and an external RF source $ {V}_{RF} $. These two sources are combined through bias-T and the source voltage can be expressed with $ {V}_{S}=V_{DC}+{V}_{RF} $. Due to existence of wire impedance there will be voltage drop on it, so the voltage at node 0 is not equal to source voltage $ {V}_{S} $.
% Boundary condition figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{images/pi_representation.pdf}
\caption{Schematic of cascade $\pi$ network representation and Thévenin equivalent circuit. }
\label{fig:BoundaryCondition}
\end{center}
\end{figure}

@@

\subsection{Distributed components}
The involvement of transmission line requires distributed component parameters. Except for distributed conductance G', which will be calculated in optical part, distributed resistance R', distributed inductance L' as well as distributed capacitance C' still need to be determined. They can be either calcuted as convertial passive components (plane resistor, parallel plane capacitor and inductor), or extracted from S-Parameter, which can be directly measured with network analyser. The former methode is simple and also don't require any extra tests, but could lead to large error due to neglection of fringe effect\cite{pillai1970fringing} as well as high frequency influence. The latter is based on experiments, so shows higher accuracy compared with former, but requires extra experiments as well as equipment, which is not always feasible for simulation research. In this work, these parameters of distributed components were eliminated by simple physical calculation assuming that device is with infinite length.

@@

Now that pure ac component cannot be simply obtained while resistance of transmission line at high frequency muss be taken into consideration, the problem was solved in another way by compromise. Instead of directly separating ac and dc component, temporal difference of ac component between adjacent time steps is considered to be feasible solution, which can be simply obtained by subtracting of Eqn. (\ref{eq:TLequation3}) at time ($n+\frac{1}{2}$) with that equation at previous time step ($n+\frac{1}{2}$), leading to:
\begin{equation}
\frac { { V }_{ j+1 }^{ n+\frac{3}{2} }-{ V }_{ j }^{ n+\frac{3}{2}}-({ V }_{ j+1 }^{ n+\frac{1}{2} }-{ V }_{ j }^{ n+\frac{1}{2} }) }{ \Delta x } \approx -L'\frac { { I }_{ j+\frac{1}{2} }^{ n+2 }-2{ I }_{ j+\frac{1}{2} }^{ n+1 }+{ I }_{ j+\frac{1}{2} }^{ n } }{ \Delta t } -R' (\widetilde{ i } _{ j+\frac{1}{2} }^{ n+\frac{3}{2} }-\widetilde{ i } _{ j+\frac{1}{2} }^{ n+\frac{1}{2} })\label{Eq:TL_substraction}
\end{equation}
The idea is, dc component as well as ac component with low frequency remains nearly unchanged after extremely short time step $\Delta t$ which is shorter than picosecond ($10^{-12}$ second) in this modeling. The variation of whole current at node $j+\frac{1}{2}$ is mainly resulting from variation of ac component of high frequency, which plays a key roll for increase of metal resistance. Hence, the variation of ac component can be approximately replaced with its corresponding variation of whole current. Besides, the current components have to be averaged in time with central difference method for sake of consistence, the same with $J_{j}^{n}$, leading to:
\begin{equation}
\tilde{ i }_{ j+\frac { 1 }{ 2 }  }^{ n+\frac{3}{2} }-\tilde{ i }_{ j+\frac { 1 }{ 2 }  }^{ n+\frac{1}{2} }\approx{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+\frac{3}{2} }-{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+\frac{1}{2} } \approx \frac{{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+2 }+{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+1 }-({ I }_{ j+\frac { 1 }{ 2 }  }^{ n+1 }+{ I }_{ j+\frac { 1 }{ 2 }  }^{ n })}{2}\label{Eq:ac_Current}
\end{equation}
Then substituting the approximate treatment above to Eqn. (\ref{Eqn:TL_substraction}),  a equation with only voltage and whole current can be obtained:
\begin{equation}
\frac { { V }_{ j+1 }^{ n+\frac{3}{2} }-{ V }_{ j }^{ n+\frac{3}{2}}-({ V }_{ j+1 }^{ n+\frac{1}{2} }-{ V }_{ j }^{ n+\frac{1}{2} }) }{ \Delta x } \approx -L'\frac { { I }_{ j+\frac{1}{2} }^{ n+2 }-2{ I }_{ j+\frac{1}{2} }^{ n+1 }+{ I }_{ j+\frac{1}{2} }^{ n } }{ \Delta t } -R' \frac{{ I }_{ j+\frac { 1 }{ 2 }  }^{ n+2 }-{ I }_{ j+\frac { 1 }{ 2 }  }^{ n }}{2}
\end{equation}

@@

\section{Results}
The amount of simulated iterations are 400 roundtrips, and during each simulation those important variables (e.g. optical field $E_{z}$, voltage, current, current density) at the middle point (x=L/2) of QCL were recorded after every time step.
\subsection{Characteristics of QCL}
Fig. \ref{fig:IVcurve} shows the voltage-current–luminance characteristics of the simulated QCL, which was obtained by supplying the QCL with a series of voltages ranging from 7.4 V to 10.8 V. The threshold voltage $V_{th}$ of the QCL is about 8.3 V, which means, under that there will be no lasing. Starting from $V_{th}$, the output emission will increase exponentially with higher voltage until tunneling phenomena occurs. At this area, QCL owns negative differential resistance (NDR) which is similar with tunneling diode. A large amount of injected electrons will directly pass active region through tunneling rather than transition from upper and lower laser levels accompanied with emission of photons. Therefore, the increasing input voltage will not contribute to laser output power.

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{images/IVCURVE.pdf}
\caption{voltage-current-luminance characteristics of simulated QCL.}
\label{fig:IVcurve}
\end{center}
\end{figure}

Besides, the roundtrip frequency of this QCL was obtained by Fourier transformation of both its optical field and electrical voltage. As Fig. \ref{fig:beatnote_noRF} shows the beatnote of simulated QCL without RF source, its roundtrip frequency $f_{rt}$ is about 13.34 GHz.
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{images/Beatnote_noRF.pdf}
\caption{Beatnote of the simulated QCL without RF source. Its roundtrip frequency $f_{rt}$ is about 13.34 GHz.}
\label{fig:beatnote_noRF}
\end{center}
\end{figure}

@@

Before simulation was carried out, firstly two parameters ($M_{A}$ and $f_{RF}$) have to be roughly defined. Although the function of RF source is known with $V_{RF}^{n}=M_{A}\cos(2\pi f_{RF}n\Delta t)$ and its power is proportional to square of its amplitude $M_{A}$, the injected power to QCL can still not be determined before simulation. Due to reflection as well as attenuation on wire between RF source and QCL, the injected power should be smaller than the power coming from RF source. But it is well known that theoretically optimal modulation frequency should exactly at roundtrip frequency. Therefore, simulations with different power and certain $f_{RF}$ were firstly carried out.
\subsubsection{Modulation with different power} 
Lack of sufficient modulation power, QCLs can still not be mode-locked even if modulation frequency is equal to $f_{rt}$. Therefore, modulations with different RF amplitude ($M_{A}$) was investigated, in which they all have the same modulation frequency and all the other parameters are the same as well. With increasing modulation power the side modes around main mode were strengthened (See Fig. \ref{fig:modA_Beatnote}) and will contribute to generate ultra short pulse. The bandwidth of frequency spectra was increasing consequently from 40 GHz to larger than 100 GHz. The optical field was mode-locked at modulation frequency $f_{RF}$, which is set at 13.9 GHz and a little higher than roundtrip frequency of this laser. 
%\begin{figure}[htbp]
%\begin{center}
%\includegraphics[scale=0.28]{images/modA_spectra.pdf}
%\caption{Normalized spectra in time as well as frequency domain with different modulation powers. modA denotes RF amplitude. $f_{RF}$ of RF source is at roundtrip frequency and QCL is bias by 8.6 kV/cm}
%\label{fig:modA_fspectra}
%\end{center}
%\end{figure}
\begin{figure*}[htbp]
  \centering
  \subfigure[]{\includegraphics[scale=0.9]{images/fa.pdf}}
  \subfigure[]{\includegraphics[scale=0.9]{images/Ba.pdf}}
\caption{(a)Frequency spectra of QCL emission with increasing modulation power from -8.5 dBm to -0.8 dBm. The simulated QCL has optical emission frequency of 3.8 THz. (b) Beatnote of optical field $E_{z}$ (dashed blue line) and electrical voltage $V\_{TL}$ (red solid line).}
\label{fig:modA_Beatnote}
\end{figure*}

@@

Similar with in modulation with different powers, frequency spectra and beatnote were used to check the influence and whether mode-locking was achieved. If no RF source exists, QCL emits continuous light as expected and will show a clear single peak in frequency domain (See Fig. \ref{fig:modA_Beatnote}), which is at its emission frequency (in this case 3.8 THz). With increasing modulation frequency, the bandwidth of their frequency spectra were also increased and optical field was mode-locked at $f_{RF}$.
\begin{figure*}[htbp]
  \centering
  \subfigure[]{\includegraphics[scale=0.9]{images/f.pdf}}
  \subfigure[]{\includegraphics[scale=0.9]{images/B.pdf}}
\caption{(a)Frequency spectra of QCL emission with increasing modulation frequency from -8.5 dBm to -0.8 dBm. The simulated QCL has optical emission frequency of 3.8 THz. (b) Beatnote of optical field $E_{z}$ (dashed blue line) and electrical voltage $V\_{TL}$ (red solid line).}
\label{fig:modA_Beatnote}
\end{figure*}
